---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggparallel

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/ggparallel)](https://CRAN.R-project.org/package=ggparallel)
[![CRAN RStudio mirror downloads](https://cranlogs.r-pkg.org/badges/last-month/ggparallel?color=blue)](https://r-pkg.org/pkg/ggparallel)
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-yellowgreen.svg)](https://github.com/heike/x3ptools/commits/main)
[![Codecov test coverage](https://codecov.io/gh/heike/ggparallel/branch/master/graph/badge.svg)](https://app.codecov.io/gh/heike/ggparallel?branch=master)
[![R-CMD-check](https://github.com/heike/ggparallel/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/heike/ggparallel/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->


The R package `ggparallel` implements and combines different types of parallel coordinate plots for categorical data: [hammock plots](http://www.schonlau.net/publication/03jsm_hammockplot_old.pdf), [parallel sets plots](https://datavizcatalogue.com/methods/parallel_sets.html), and [common angle plots](https://ieeexplore.ieee.org/document/6634157), as well as common angle plots with a hammock-like adjustment for line widths.

## Installation

The package is available on CRAN:

```
install.packages("ggparallel")
```

You can install the development version of ggparallel from [GitHub](https://github.com/) with:

```
# install.packages("remotes")
remotes::install_github("heike/ggparallel")
```

## Basic use case



```{r}
library(ggparallel)
data(mtcars)

ggparallel(list("gear", "cyl"), data=mtcars)
```


```{r}
ggparallel(list("gear", "cyl"), data=mtcars, method="hammock", ratio=0.25)
```





